Data Preparation

### 2019-02-15 Data Preparation.Rmd
minor change

```{r import d_transcript, cache = TRUE}
d_transcript <- rbind(
  read_csv(
    "./Input/Raw Grades/grades1.csv",
    col_types = cols(
      `Program (Abbreviation)` = col_character(),
      `Appraisal Status` = col_character(),
      `Module Booking Reason (Description)` = col_character(),
      `Object name` = col_character(),
      `Start date` = col_character(),
      `End Date` = col_character()
      )
    ),
  read_csv(
    "./Input/Raw Grades/grades2.csv",
    col_types = cols(
      `Program (Abbreviation)` = col_character(),
      `Appraisal Status` = col_character(),
      `Module Booking Reason (Description)` = col_character(), 
      `Object name` = col_character(), 
      `Start date` = col_character(), 
      `End Date` = col_character()
      )
    )
  )
```

@@

### Selecting Variables

@@

  # folowing guidelines of Richard Vos, only consider: `Appraisal (Description)` == "Grade supervisor" and 
  filter(
    `Appraisal (Description)` == "Grade supervisor",
    `Appraisal Type`          == "7055" # removes ~ 15 observations

>>>>

```{r import d_transcript, cache = TRUE}
d_transcript <- rbind(
  read_csv(
    "./Input/Raw Grades/grades1.csv",
    col_types = cols(
      `Program (Abbreviation)` = col_character(),
      `Appraisal Status` = col_character(),
      `Module Booking Reason (Description)` = col_character(),
      `Object name` = col_character(),
      `Start date` = col_character(),
      `End Date` = col_character()
      )
    ),

  read_csv(
    "./Input/Raw Grades/grades2.csv",
    col_types = cols(
      `Program (Abbreviation)` = col_character(),
      `Appraisal Status` = col_character(),
      `Module Booking Reason (Description)` = col_character(), 
      `Object name` = col_character(), 
      `Start date` = col_character(), 
      `End Date` = col_character()
      )
    )

@@

@@

  # folowing guidelines of Richard Vos, we only consider: `Appraisal (Description)` == "Grade supervisor" and `Appraisal Type`          == "7055"
  filter(
    `Appraisal (Description)` == "Grade supervisor",
    `Appraisal Type`          == "7055" # removes ~ 15 observations
  ) %>%
